---
output: html_document

params:
  TIME: NA
  APP_DEV: NA
  APP_DEV_SHORT: NA
  APP_NAME: NA
  APP_NAME_SHORT: NA
  APP_VER: NA
  APP_LINK: NA
  calibrationCurveData: NA
  calibrationCurveDataReformatted: NA
  externalStandardErrorData: NA
  methodPrecisionData: NA
  standardSolutionData: NA
  standardSolutionEquipmentData: NA
  samplePreparationData: NA
  homogeneityData: NA
  inputWeightLeastSquared: NA
  customWls: NA
  customWlsPooled: NA
  inputCaseSampleReplicates: NA
  inputCaseSampleMeanConcentration: NA
  inputCaseSampleMeanPeakAreaRatio: NA
  inputCaseSampleWeight: NA
  inputConfidenceInterval: NA
  inputManualCoverageFactor: NA
  uncCalibrationCurve: NA
  uncMethodPrecision: NA
  uncStandardSolution: NA
  uncSamplePreparation: NA
  uncHomogeneity: NA
  homogeneityTestResult: NA
  homogeneityTestAlphaValue: NA
  homogeneityTestDofW: NA
  homogeneityTestDofB: NA
  homogeneityTestFStat: NA,
  homogeneityTestFCrit: NA
  combinedUncertaintyResult: NA
  coverageFactorResult: NA
  expandedUncertaintyResult: NA
  expandedUncertaintyResultPercentage: NA
  
  homogeneity_standardUncertainty_left_renderer: NA
  homogeneity_standardUncertainty_right_renderer: NA
  homogeneity_standardUncertainty_max_renderer: NA
  homogeneity_relativeStandardUncertainty_renderer: NA
  
  homogeneityTest_fValue_renderer: NA
  homogeneity_fCritical_renderer: NA
  renderHomogeneityTestAnswer: NA
  
  outputPooledStandardDeviation_renderer: NA
  outputStandardUncertainty_renderer: NA
  outputRealtiveStandardUncertainties_renderer: NA
  methodPrecision_finalAnswer_bottom_renderer: NA
  
  standardSolution_solutionRelativeStandardUncertainty_renderer: NA
  standardSolution_finalAnswer_renderer: NA
  
  samplePreparation_standardUncertainty_renderer: NA
  samplePreparation_relativeStandardUncertainty_renderer: NA
  samplePreparation_finalAnswer_bottom_renderer: NA
  
  combinedUncertainty_finalAnswer_renderer: NA
  coverageFactor_effectiveDegreesOfFreedom_renderer: NA
  expandedUncertainty_finalAnswer_renderer: NA
  
title: "`r params$APP_NAME` Report"
---

<!--
###########################################################################
#
# Measurement Uncertainty Calculator - Copyright (C) 2019
# Leverhulme Research Centre for Forensic Science
# Roy Mudie, Joyce Klu, Niamh Nic Daeid
# Website: https://github.com/LRCFS/lrcfs-measurement-uncertainty-calculator/
# Contact: lrc@dundee.ac.uk
#
# This program is free software: you can redistribute it and/or modify
# it under the terms of the GNU Affero General Public License as published
# by the Free Software Foundation, either version 3 of the License, or
# (at your option) any later version.
#
# This program is distributed in the hope that it will be useful,
# but WITHOUT ANY WARRANTY; without even the implied warranty of
# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
# GNU Affero General Public License for more details.
#
# You should have received a copy of the GNU Affero General Public License
# along with this program.  If not, see <https://www.gnu.org/licenses/>.
#
###########################################################################
-->

```{css, echo=FALSE}
.icon-large{
  display: none;
}
```

## `r params$APP_DEV`

#### Report Generated: `r params$TIME`

#### Software Version: `r params$APP_NAME` (v`r params$APP_VER`)

This report was automatically generated on `r params$TIME` using the using the `r params$APP_DEV_SHORT` `r params$APP_NAME` (v`r params$APP_VER`) available at `r params$APP_LINK`.

***

## Authorisation 

### Report Author
| Name | Signature | Job Title / Position | Date |
|------|-----------|----------------------|------|
|&nbsp;|           |                      |      |
|&nbsp;|           |                      |      |
|&nbsp;|           |                      |      |

### Approval 
| Name | Signature | Job Title / Position | Date |
|------|-----------|----------------------|------|
|&nbsp;|           |                      |      |
|&nbsp;|           |                      |      |
|&nbsp;|           |                      |      |

\newpage

## Summary
The following is a summary of the supplied data and results calculated.

### Results
### Homogeniety Test
Where data has been provided for a Homogeneity test the following results were recorded:

|Property                   |Value                                |
|---------------------------|-------------------------------------|
|Alpha Value                |`r params$homogeneityTestAlphaValue` |
|Degrees of Freedom Within  |`r params$homogeneityTestDofW`       |
|Degrees of Freedom Between |`r params$homogeneityTestDofB`       |
|F Statistic                |`r params$homogeneityTestFStat`      |
|F Critical                 |`r params$homogeneityTestFCrit`      |

#### **Result: `r params$homogeneityTestResult`**
***
\newpage

### Results
### Measurement Uncertainty

#### Inputs
The results of this report are made using the follow supplied information.

| Input                             | Value Specified                            |
|-----------------------------------|--------------------------------------------|
|Weighted Least Square Regression   |$`r params$inputWeightLeastSquared`$        |
|Case Sample Replicates             |`r params$inputCaseSampleReplicates`        |
|Case Sample Mean Concentration     |`r params$inputCaseSampleMeanConcentration` |
|Case Sample Mean Peak Area Ratio   |`r params$inputCaseSampleMeanPeakAreaRatio` |
|Case Sample Weight                 |`r params$inputCaseSampleWeight`            |
|Confidence Level                   |`r params$inputConfidenceInterval`          |
|Manually Specified Coverage Factor |`r params$inputManualCoverageFactor`        |
|Homogeneity Test Alpha value       |`r params$homogeneityTestAlphaValue`        |

***

#### Individual Uncertainty Components

The calculated results for each individual component are shown below.

| Uncertainty Component | Relative Standard Uncertainty |
|-----------------------|-------------------------------|
|Homogeneity            |`r params$uncHomogeneity`      |
|Calibration Curve      |`r params$uncCalibrationCurve` |
|Method Precision       |`r params$uncMethodPrecision`  |
|Calibration Standard   |`r params$uncStandardSolution` |
|Sample Preparation     |`r params$uncSamplePreparation`|

#### Overall Uncertainty
| Attribute             | Value                                        |
|-----------------------|----------------------------------------------|
|Combined Uncertainty   |`r params$combinedUncertaintyResult`          |
|Coverage Factor        |`r params$coverageFactorResult`               |
|Expanded Uncertainty   |`r params$expandedUncertaintyResult`          |
|% Expanded Uncertainty |`r params$expandedUncertaintyResultPercentage`|

With the information supplied above the following result has been concentration result has been calculated.

#### **Result: Concentration = `r params$inputCaseSampleMeanConcentration` $\pm$ `r params$expandedUncertaintyResult`**
***

\newpage

# Appendix 1 - Methodology

## Homogeneity Test

### Overview

A one-way analysis of variance (ANOVA) is used to test the null hypotheses \((H_0)\) of equality of means among sample groups against the alternative hypothesis \((H_1)\) that at least two of the group means differ, on the assumption that samples are normally distributed, have equal variance and are independent. For \(k\) independent groups with means \(m_1 \ldots m_k\), the hypothesis of interest is given by:

\(H_0\): \(m_1 = m_2 = m_3= \ldots = m_k\)

\(H_1\): \(m_l \neq m_j\) for some \(l,j\)

The F statistic \((F_{\large s})\) under \(H_0\) follows an F-distribution given by the ratio of mean sum of squares between \((MSS_B)\) and mean sum of squares within \((MSS_W)\), as shown in the Method tab.

The \(H_0\) is rejected if the F statistic \((F_{\large s})\) is greater than the F critical (\(F_c\)) value for a given alpha level and conclude that at least two group means differ. For more information see <a href='https://www.researchgate.net/publication/226708564_Uncertainty_calculations_in_the_certification_of_reference_materials_1_Principles_of_analysis_of_variance' target='_blank'>Veen et al: Principles of analysis of variance (2000)</a> and <a href='https://www.researchgate.net/publication/226313972_Uncertainty_calculations_in_the_certification_of_reference_materials_2_Homogeneity_study' target='_blank'>Veen et al: Homogeneity study (2001)</a>.


### Method

A <a href='https://en.wikipedia.org/wiki/Analysis_of_variance' target='_blank'>one-way analysis of variance (ANOVA)</a> test is carried out where the Mean Sum of Squares Between (\(MSS_B\)) is defined as:

$MSS_B = \frac{ \sum\limits_{j=1}^k n_j(\overline{X}_{j}-\overline{X}_T)^2 } { k-1 },$ the Mean Sum of Squares Within (\(MSS_W\)) is defined as: $MSS_W = \frac{ \sum\limits_{j=1}^k\sum\limits_{i=1}^{n_j} (X_{ij}-\overline{X}_j)^2 } { N-k }$

and the F statistic (or F value)  is given by: $F_{\large s} = \frac{MSS_B}{MSS_W}$

Finally, \(H_0\) is rejected if \(F_{\large s} > F_c\)

- \(H_0\) is the null hypotheses of equal group means.

- \(k\) is the number of groups.

- \(n_j\) is the number of measurements/replicates in the group \(j\) where \(j=1\ldots k\).

- \(N\) total number of measurements, i.e. \(N = \sum\limits_{j=1}^k n_j\)

- \(F_{\large s}\) is the F statistic calculated from the supplied data.

- \(F_c\) is the critical value from <a href='https://www.statisticshowto.com/tables/f-table/' target='_blank'>F-Distribution Table</a> at a given alpha level, i.e. \(F_{{\LARGE\nu}_B,{\LARGE\nu}_W,\alpha}\)),

- \({\LARGE\nu}_B\) is the degrees of freedom for the between-group, calculated as \(k-1\).

- \({\LARGE\nu}_W\) is the degrees of freedom for the within-group, calculated as \(N-k\).

- \(X_{ij}\) is the \(i^{th}\) measurement of the \(j^{th}\) group.

- \(\overline{X}_j\) is the mean of measurement in group \(j\).

- \(\overline{X}_T\) is the grand mean of all measurements.

***
\newpage

## Homogeneity

### Overview
Homogeneity/heterogeneity as defend in <a href='https://eurachem.org/images/stories/Guides/pdf/UfS_2019_EN_P2.pdf' target='_blank' title='Measurement uncertainty arising from sampling: A guide to methods and approaches'>EURACHEM/CITAC guide (2019)</a> and <a href='http://publications.iupac.org/pac/1990/pdf/6206x1193.pdf' title='INTERNATIONAL UNION OF PURE AND APPLIED CHEMISTRY' target='_blank'>IUPAC (1990)</a> is:

"The degree to which a property or constituent is uniformly distributed throughout a quantity of material.
Note:

- A material may be homogeneous with respect to one analyte or property but heterogeneous with respect to another.

- The degree of heterogeneity (the opposite of homogeneity) is the determining factor of sampling error."

The <a href='https://link.springer.com/article/10.1007/s007690000238' target='_blank' title='Uncertainty calculations in the certification of reference materials. 2. Homogeneity study'>uncertainty of homogeneity (2001)</a> quantifies the uncertainty associated with the between-group homogeneity where differences among sample groups are of interest.  Detailed step-by-step calculations are displayed here with the main formulas used to compute the uncertainty of homogeneity shown in the Method tab.
To find out whether your samples are homogenous or heterogenous, the Homogeneity Test tab displays a detailed calculation for testing whether there is a statistically significant difference between group means of samples using a one-way analysis of variance (ANOVA) on the assumption that samples are normally distributed, have equal variance and are independent.

### Method
The Relative Standard Uncertainty of homogeneity is given by the following calculation:
\(u_r(\text{Homogeneity}) = \frac{ \text{Standard Uncertainty} }{ \text{Grand Mean} } = \frac{ u(\text{Homogeneity}) }{ \overline{X}_T } \)

where \(\displaystyle u(\text{Homogeneity}) = \text{max}\{u_a,u_b\},\)

\(\displaystyle u_a(\text{Homogeneity}) = \sqrt{\frac{ MSS_B - MSS_W }{ n_0 }}\) and \(\displaystyle u_b(\text{Homogeneity}) = \sqrt{ \frac{ MSS_W }{ n_0 } } \times \sqrt{ \frac{ 2 }{ k(n_0-1) } }\)

A <a href='https://en.wikipedia.org/wiki/Analysis_of_variance' target='_blank' title='Analysis of variance'>one-way analysis of variance (ANOVA)</a> test is carried out to calculate the Mean Sum of Squares Between groups (\(MSS_B\)) and the Mean Sum of Squares Within groups (\(MSS_W\)) given by:
\(\displaystyle MSS_B = \frac{ \sum\limits_{j=1}^k n_j(\overline{X}_{j}-\overline{X}_T)^2 } { k-1 } \) and \(\displaystyle MSS_W = \frac{ \sum\limits_{j=1}^k\sum\limits_{i=1}^{n_j} (X_{ij}-\overline{X}_j)^2 } { N-k }\)

- \(k\) is the number of groups.
- \(n_j\) is the number of measurements/replicates in the group \(j\) where \(j=1\ldots k\).
- \(\displaystyle n_0 = \frac{1}{k-1} \left[\sum\limits_{j=1}^k n_j - \frac{ \sum\limits_{j=1}^k n_j^2 } { \sum\limits_{j=1}^k n_j }\right] = \frac{1}{k-1} \left[ N - \frac{A}{N} \right] \) <br />Where all \(n_j\)'s are the same (i.e. \(n_1=n_2=\ldots=n_k=n\)) then this simplifies to \(n_0 = n\).
- \(N\) is the total number of measurements, i.e. \(N = \sum\limits_{j=1}^k n_j\).
- \(A\) is the sum of squared number of measurements/replicates in the group, i.e. \(A = \sum\limits_{j=1}^k n^2_j\)
- \(X_{ij}\) is the \(i^{th}\) measurement of the \(j^{th}\) group.
- \(\overline{X}_j\) is the mean of measurement in group \(j\).
- \(\overline{X}_T\) is the grand mean, calculated as the sum of all measurements \(\left(\sum\limits_{j=1}^k\sum\limits_{i=1}^{n_j} X_{ij}\right)\) divided by the number of measurements \((N)\).


***
\newpage 

## Calibration Curve

### Overview
All computations and details of formulas used for computing the uncertainty of the calibration curve are displayed here. This version of the software assumes a linear calibration curve with the option to specify weights if weighted least squares (WLS) regression is required.
The Method tab shows the main formulas used to compute the uncertainty of the calibration curve for both weighted and non-weighted least squares regression. All calculations preformed in this application use the WLS formula which is equivalent to a simple linear regression (non-weighted) formula if the weight \(W=1\) is specified.

### Method
#### Weighted
Where a weight \(W \neq 1\) is specified the uncertainty of calibration curve is given by:
$u\text{(CalCurve)} = \frac{S_{w}}{b_1} \sqrt{\frac{1}{w_{s}(r_s)} + \frac{1}{n} + \frac{(x_s - \overline{x}_w)^2}{S_{{xx}_w}} }$
where \(S_w\) is the standard error of regression given by
$S_w = \sqrt{\frac{\sum\limits_{i=1}^n w_i(y_i-\hat{y}_i)^2}{n-2}}$
The Relative Standard Uncertainty is then calculated as:
$u_r\text{(CalCurve)} = \frac{\text{Standard Uncertatiny}}{\text{Case Sample Mean Concentration}} = \frac{u\text{(CalCurve)}}{x_s}$

 - \(x_i\) concentration at level \(i\).
 - \(x_s\) is the mean concentration of the Case Sample.
 - \(r_s\) is the number of replicates made on test sample to determine \(x_s\).
 - \(y_i\) observed peak area ratio for a given concentration \(x_i\).
 - \(\hat{y}_i\) predicted value of \(y\) for a given value \(x_i\).
 - \(b_1\) is the Slope of the of the weighted regression line.
 - \(y_s\) is the mean of Peak Area Ratio of the Case Sample.
 - \(n\) is the number of measurements used to generate the Calibration Curve.
 - \(\overline{x}_w\) is the mean values of the different calibration standards.
 - \(W\) is the specified Weight.
 - \(w\) is the standardised weight given by \(W(\frac{n}{\sum{W}})\)
 - \(w_s\) is the Weight of Case Sample.
 - \(S_{{xx}_w}\) is the sum of squares deviation of \(x\) given by \(\sum\limits_{i=1}^n w_i(x_i - \overline{x})^2\).

#### Non Weighted
When a weight of \(W = 1\) is specified the uncertainty is simplified to the following:
$u\text{(CalCurve)} = \frac{S_{y/x}}{b_1} \sqrt{\frac{1}{r_s} + \frac{1}{n} + \frac{(x_s - \overline{x})^2}{S_{xx}}}$
where \(S_{y/x}\) is the standard error of regression given by
$S_{y/x} = \sqrt{\frac{\sum\limits_{i=1}^n(y_i-\hat{y}_i)^2}{n-2}}$
The Relative Standard Uncertainty is then calculated as:
$u_r\text{(CalCurve)} = \frac{\text{Standard Uncertatiny}}{\text{Case Sample Mean Concentration}} = \frac{u\text{(CalCurve)}}{x_s}$

 - \(b_1\) is the Slope of the of regression line.
 - \(\overline{x}\) is the mean values of the different calibration standards.
 - \(S_{xx}\) is the sum of squares deviation of \(x\) given by \(\sum\limits_{i=1}^n (x_i - \overline{x})^2\).
 
***
\newpage 
## Method Precision

### Overview

A step-by-step approach for estimating the uncertainty of method precision is outlined here. The main methodology used is the pooled standard deviation approach.

Where a precision experiment is carried out for different nominal values of concentration (e.g. low, medium and high), the uncertainty of method precision is calculated for each nominal value separately and the uncertainty used for the combined uncertainty is the value for which the specified case sample concentration is closest to the nominal value.

To derive the relative standard uncertainty, the standard uncertainty is divided by the number of case sample replicate as recommended by <a href='https://www.sciencedirect.com/science/article/abs/pii/S0021967317304909' target='_blank' title='Evaluation of the measurement uncertainty: Some common mistakes with a focus on the uncertainty from linear calibration'>Kadis (2017)</a>.)

### Method

The Relative Standard Uncertainty of method precision is given by:
$u_r(\text{MethodPrec})_{\text{(NV)}} = \frac{S_{p\text{(NV)}}}{\overline{x}_{\text{(NV)}}\sqrt{r_s}} = \frac{u(\text{MethodPrec})_{\text{(NV)}}}{\overline{x}_{\text{(NV)}}},$

where

$u(\text{MethodPrec})_{\text{(NV)}} = \frac{S_{p\text{(NV)}}}{\sqrt{r_s}},$

and

$S_{p(\text{NV})} = \sqrt{\frac{\sum{(S^2 \times {\large\nu})_{\text{(NV)}}}}{\sum {\large\nu}_{\text{(NV)}}}}.$

- \(S\) is the standard deviation for each run.

- \({\large\nu}\) is the individual degrees of freedom.

- \(S_p\) is the pooled standard deviation.

- \(NV\) is the nominal value of concentration.

- \(\overline{x}_{\text{(NV)}}\) is the mean concentration for the nominal value \(\text{NV}\).

***
\newpage 
## Calibration Standard

### Overview

Information provided on the structure of solution preparation and details of used equipment is displayed here, along with a step-by-step calculation of the uncertainty associated with spiking the calibration standards.

The solution structure is displayed using a network or tree diagram with the root assumed to be the reference compound and the final nodes are assumed to be the spiking range for calibrators used in generating the calibration curve.

If more than one spiking range exists (which may be due to splitting the range of the calibration curve), the uncertainty associated with the calibration standard is computed by pooling the relative standard uncertainties associated with preparing solutions and spiking the calibration curve.

### Method

The Relative Standard Uncertainty (RSU) of each equipment is computed using:

$u_r(\text{Equipment}) = \frac{\frac{\text{Tolerance}}{\text{Coverage Factor}}}{\text{Volume}}$

The RSU of reference compound is calculated using:

$u_r(\text{Reference Compound}) = \frac{\frac{\text{Tolerance}}{\text{Coverage Factor}}}{\text{Purity}}$

The RSU of each solution is computed using:

$u_r\text{(WorkingSolution)} = \sqrt{u_r\text{(Parent Solution)}^2 + \sum{[u_r\text{(Equipment)}^2_{\text{(Vol,Tol)}} \times N\text{(Equipment)}_{\text{(Vol,Tol)}}]}}$

The RSU of standard (spiking) solution is obtained by pooling the RSU's of the calibration curve spiking range.

$u_r(\text{CalStandard}) = \sqrt{\sum{u_r\text{(Calibration Curve Spiking Range)}^2}}$

- \(\text{Parent Solution}\) is the solution from which a given solution is made.

- \(N\text{(Equipment)}\) is the number of times a piece of equipment is used in the preparation of a given solution.

***
\newpage 
## Sample Preparation

### Overview

Uncertainty of sample preparation combines uncertainty sources from the use of different equipment in preparing the sample, such as weighing balance, pipette and volumetric flask.

### Method

The Relative Standard Uncertainty (RSU) of each equipment is computed using:

$u_r(\text{Equipment}) = \frac{\frac{\text{Tolerance}}{\text{Coverage Factor}}}{\text{Capacity}}$

The RSU of sample preparation is given by:

$u_r\text{(SamplePreparation)} = \sqrt{\sum{[u_r(\text{Equipment})_{\text{(Cap,Tol)}}^2 \times N(\text{Equipment})_{\text{(Cap,Tol)}}}]}$

- \(N\text{(Equipment)}\) is the number of times a piece of equipment is used in taking the preparation of a given sample.

***
\newpage 
## Combined Uncertainty

### Overview

The combined uncertainty is obtained by combining all the individual uncertainty components.

If data is uploaded for all the uncertainty components; Homogeneity, Calibration Curve, Method Precision, Calibration Standard and Sample Preparation, relative standard uncertainty is computed for each uncertainty component and are combined to obtain the Combined Uncertainty of the analytical process.

If data is omitted for some uncertainty components, NA's will be displayed for those components and the Combined Uncertainty will only take into account components for which data is provided.

### Method
The combined uncertainty is given by:

$\text{CombUncertainty} = x_s \sqrt{\sum{u_r\text{(Individual Uncertainty Component)}^2}}$

- \(x_s\) is the Case Sample Mean Concentration.

***
\newpage 
## Coverage Factor

### Overview

Coverage factor \((k)\) is a number usually greater than one from which an expanded uncertainty is obtained when \(k\) is multiplied by a combined standard uncertainty. To determine a suitable coverage factor, a specified level of confidence is required along with knowledge about the degrees of freedom of all uncertainty components.

An effective degrees of freedom is computed using the <a href='https://www.iso.org/sites/JCGM/GUM/JCGM100/C045315e-html/C045315e_FILES/MAIN_C045315e/AG_e.html' target='_blank' title='Annex G: Degrees of freedom and levels of confidence'>Welch-Satterthwaite equation (JCGM 100:2008)</a> with details given in the Method tab. The derived effective degrees of freedom along with the specified \({\small CI\%}\) is used to read a value (termed coverage factor) from the T-Distribution Table.)

### Method

The effective degrees of freedom \(({\LARGE\nu}_{\text{eff}})\) using Welch-Satterthwaite approximation for <em>relative</em> standard uncertainty is given by:

${\LARGE\nu}_{\text{eff}} =\frac{(\frac{\text{CombUncertainty}}{x_s})^4}{\sum{\frac{u_r\text{(Individual Uncertainty Component)}^4}{{\LARGE\nu}_{\text{(Individual Uncertainty Component)}}}}}$

The coverage factor \((k_{{\large\nu}_{\text{eff}}, {\small CI\%}})\) is read from the T-Distribution Table using the calculated \({\Large\nu}_{\text{eff}}\) and specified \({\small CI\%}\).

- \(x_s\) is the Case Sample Mean Concentration.

- \(\nu\) is the Degrees of Freedom for each uncertainty component.

- \({\small\text{CombUncertainty}}\) is the Combined Uncertainty of the individual uncertainty components.

***
\newpage

## Expanded Uncertainty

### Overview

The expanded uncertainty  is the final step of measurement uncertainty computation. This is done in order to derive a confidence interval believed to contain the true unknown value.

It is computed by multiplying the Combined Uncertainty \((\text{CombUncertainty})\) with the coverage factor \((k_{{\large\nu}_{\text{eff}}, {\small CL\%}})\).

### Method

The expanded uncertainty \(\text{(ExpUncertainty)}\) is given by:

$\text{ExpUncertainty} = k_{{\large\nu}_{\text{eff}}, {\small CL\%}} \times \text{CombUncertainty}$

with percentage expanded uncertainty given by:

$\text{%ExpUncertainty} = \frac{\text{ExpUncertainty}}{x_s} \times 100$

where:

- \(k_{{\large\nu}_{\text{eff}}, {\small CL\%}}\) is the coverage factor based on effective degrees of freedom and specified confidence interval percentage.

- \({\small\text{CombUncertainty}}\) is the combined uncertainty.

- \(x_s\) case sample mean concentration.

***
\newpage 

# Appendix 2 - Calculations
## Homogeneity Test
`r params$homogeneityTest_fValue_renderer`

***
`r params$homogeneity_fCritical_renderer`

***
`r params$renderHomogeneityTestAnswer`

***
\newpage 

## Homogeneity
`r params$homogeneity_standardUncertainty_left_renderer`

***
`r params$homogeneity_standardUncertainty_right_renderer`

***
`r params$homogeneity_standardUncertainty_max_renderer`

***
`r params$homogeneity_relativeStandardUncertainty_renderer`

***
\newpage 

## Calibration Curve
***
\newpage

## Method Precision
`r params$outputPooledStandardDeviation_renderer`

***
`r params$outputStandardUncertainty_renderer`

***
`r params$outputRealtiveStandardUncertainties_renderer`

***
`r params$methodPrecision_finalAnswer_bottom_renderer`

***
\newpage 

## Calibration Standard
`r params$standardSolution_solutionRelativeStandardUncertainty_renderer`

***
`r params$standardSolution_finalAnswer_renderer`

***
\newpage 

## Sample Preparation
`r params$samplePreparation_standardUncertainty_renderer`

***
`r params$samplePreparation_relativeStandardUncertainty_renderer`

***
`r params$samplePreparation_finalAnswer_bottom_renderer`

***
\newpage 

## Combined Uncertainty
`r params$combinedUncertainty_finalAnswer_renderer`

## Coverage Factor
`r params$coverageFactor_effectiveDegreesOfFreedom_renderer`

## Expanded Uncertainty
`r params$expandedUncertainty_finalAnswer_renderer`

***
\newpage 

# Appendix 3 - Raw Data
## Homogeneity
### Homogeneity (CSV)
```{r echo=FALSE}
params$homogeneityData
```

\newpage
## Calibration Curve
### Calibration Curve (CSV)
```{r echo=FALSE}
params$calibrationCurveData
```

\newpage
### External Standard Error (CSV)
```{r echo=FALSE}
params$externalStandardErrorData
```

\newpage
### Specified Custom Weights (CSV)
```{r echo=FALSE}
params$customWls
```

\newpage
### Specified Custom Weights for Pooled External Standard Error (CSV)
```{r echo=FALSE}
params$customWlsPooled
```

\newpage
## Method Precision
### Method Precision (CSV)
```{r echo=FALSE}
params$methodPrecisionData
```

\newpage
## Calibration Standard
### Calibration Standard Structure (CSV)
```{r echo=FALSE}
params$standardSolutionData
```

### Calibration Standard Equipment (CSV)
```{r echo=FALSE}
params$standardSolutionEquipmentData
```

\newpage
## Sample Preparation
### Sample Preparation (CSV)
```{r echo=FALSE}
params$samplePreparationData
```

# END OF REPORT