### Measurement Uncertainty

#### Inputs
The results of this report are made using the follow supplied information.

| Input                             | Value Specified                            |
|-----------------------------------|--------------------------------------------|
```{r part_input_values, echo=FALSE, results="asis"}
cat(paste0("|Weighted Least Square Regression|$",params$inputWeightLeastSquared,"$|\n"))
cat("|Case Sample Replicates|",params$inputCaseSampleReplicates,"|\n")
cat("|Case Sample Mean Concentration|",params$inputCaseSampleMeanConcentration,"|\n")

if(length(params$inputCaseSampleMeanPeakAreaRatio) != 0 && params$inputCaseSampleMeanPeakAreaRatio != "" && !is.na(params$inputCaseSampleMeanPeakAreaRatio) && !is.null(params$inputCaseSampleMeanPeakAreaRatio))
{
  cat("|Case Sample Mean Peak Area Ratio|",params$inputCaseSampleMeanPeakAreaRatio,"|\n")
}

if(length(params$inputCaseSampleWeight) != 0 && params$inputCaseSampleWeight != "" && !is.na(params$inputCaseSampleWeight) && !is.null(params$inputCaseSampleWeight))
{
  cat("|Case Sample Weight|",params$inputCaseSampleWeight,"|\n")
}

if(length(params$inputConfidenceInterval) != 0 && params$inputConfidenceInterval != "" && !is.na(params$inputConfidenceInterval) && !is.null(params$inputConfidenceInterval))
{
  cat("|Confidence Level|",params$inputConfidenceInterval,"|\n")
}

if(length(params$inputManualCoverageFactor) != 0 && params$inputManualCoverageFactor != "" && !is.na(params$inputManualCoverageFactor) && !is.null(params$inputManualCoverageFactor))
{
  cat("|Manually Specified Coverage Factor|",params$inputManualCoverageFactor,"|\n")
}

if(length(params$uncHomogeneity) != 0 && params$uncHomogeneity != "" && !is.na(params$uncHomogeneity) && !is.null(params$uncHomogeneity))
{
 cat("|Homogeneity Alpha value|",params$homogeneityTestAlphaValue,"|\n")
}
```

***

#### Individual Uncertainty Components

The calculated results for each individual component are shown below.

| Uncertainty Component | Relative Standard Uncertainty |
|-----------------------|-------------------------------|
```{r part_uncertaintyComponents_results, echo=FALSE, results="asis"}
if(!is.na(params$uncHomogeneity))
{
  cat("|Homogeneity|",params$uncHomogeneity,"|\n")
}
if(!is.na(params$uncCalibrationCurve))
{
  cat("|Calibration Curve|",params$uncCalibrationCurve,"|\n")
}
if(!is.na(params$uncMethodPrecision))
{
  cat("|Method Precision|",params$uncMethodPrecision,"|\n")
}
if(!is.na(params$uncStandardSolution))
{
  cat("|Calibration Standard|",params$uncStandardSolution,"|\n")
}
if(!is.na(params$uncSamplePreparation))
{
  cat("|Sample Preparation|",params$uncSamplePreparation,"|\n")
}
``` 

#### Overall Uncertainty
| Attribute             | Value                                        |
|-----------------------|----------------------------------------------|
|Combined Uncertainty   |`r params$combinedUncertaintyResult`          |
|Coverage Factor        |`r params$coverageFactorResult`               |
|Expanded Uncertainty   |`r params$expandedUncertaintyResult`          |
|% Expanded Uncertainty |`r params$expandedUncertaintyResultPercentage`|

With the information supplied above the following result has been concentration result has been calculated.

#### **Result: Concentration = `r params$inputCaseSampleMeanConcentration` $\pm$ `r params$expandedUncertaintyResult`**
***