---
title: "LRCFS Measurement Uncertainty Report"
output: pdf_document
params:
  calibrationCurveData: NA
  calibrationCurveDataReformatted: NA
  externalStandardErrorData: NA
  methodPrecisionData: NA
  standardSolutionData: NA
  standardSolutionEquipmentData: NA
  sampleVolumeData: NA
  inputWeightLeastSquared: NA
  inputCaseSampleReplicates: NA
  inputCaseSampleMeanConcentration: NA
  inputConfidenceInterval: NA
  uncCalibrationCurve: NA
  uncMethodPrecision: NA
  uncStandardSolution: NA
  uncSampleVolume: NA
  combinedUncertaintyResult: NA
  expandedUncertaintyResult: NA
  expandedUncertaintyResultPercentage: NA
---

**Date:** 1st Jan 2019

**Report Issue Number:** 001

**Software Version:** LRCFS Measurement Uncertainty Calculator (v0.5)

The following report was generated using the using the LRCFS Measurement Uncertainty Calculator (v0.5) available at www.dundee.ac.uk/lrcfs/mucalc.

## Summary
This is a summary of the results based on the information:

**Weighted Least Square Regression:** $`r params$inputWeightLeastSquared`$

**Confidence Interval:** `r params$inputConfidenceInterval`

| Case Sample Data      | Relative Standard Uncertainty              |
|-----------------------|--------------------------------------------|
|Replicates             |`r params$inputCaseSampleReplicates`        |
|Mean Concentration     |`r params$inputCaseSampleMeanConcentration` |

### Results

| Uncertainty Component | Relative Standard Uncertainty |
|-----------------------|-------------------------------|
|Calibration Curve      |`r params$uncCalibrationCurve` |
|Method Precision       |`r params$uncMethodPrecision`  |
|Standard Solution      |`r params$uncStandardSolution` |
|Sample Volume          |`r params$uncSampleVolume`     |

#### Expanded Uncertainty: 0.59628

### Report Author
| Name | Signature | Job Title / Position | Date |
|------|-----------|----------------------|------|
|      |           |                      |      |

### Approval 
| Name | Signature | Job Title / Position | Date |
|------|-----------|----------------------|------|
|      |           |                      |      |


# Appendix 1 - Calculations

## Calibration Curve
The uncertainty of calibration curve is given by:

$$u\text{(CalCurve)} = \frac{S_{y/x}}{b_1} \sqrt{\frac{1}{r_s} + \frac{1}{n} + \frac{(x_s - \overline{x})^2}{S_{xx}}}$$

where $S_{y/x}$ is the standard error of regression given by

$$S_{y/x} = \sqrt{\frac{\sum\limits_{i=1}^n(y_i-\hat{y}_i)^2}{n-2}}$$

- $S_{y/x}$ is the standard error of regressing $y$ on $x$

- $b_1$ is the Slope of the of regression line

- $r_s$ is the number of replicates made on test sample to determine $x_s$

- $n$ is the number of measurements used to generate the Calibration Curve

- $x_s$ is the mean concentration of the Case Sample

- $\overline{x}$ is the mean values of the different calibration standards

- $S_{xx}$ is the sum of squares deviation of $x$ given by $\sum\limits_{i=1}^n (x_i - \overline{x})^2$

## Method Precision

Work in progress...

## Standard Solution

Work in progress...

## Sample Volume

Work in progress...

# Appendix 2 - Raw Data
```{r}
params$calibrationCurveData
```

```{r}
params$externalStandardErrorData
```

```{r}
params$methodPrecisionData
```

```{r}
params$standardSolutionData
```

```{r}
params$standardSolutionEquipmentData
```


```{r}
params$sampleVolumeData
```

# END REPORT



# Some Latex Test

Latex inline looks like this: $x = \sqrt{5/2}$

Latex on a new line looks like this: $$x = \sqrt{5/2}$$


